The \project{unRAVE} catalog

### 2016-09-05 article/unrave.tex
Some stubs in discussion, some banter, some ranting

We have presented an independent re-analysis of \rave\ spectra that makes near-maximal
use of the information content for red giant branch star, and provides significant a
improvement in stellar parameter ($\teff$, $\logg$, [Fe/H]) precision over previous
\rave\ data releases.  When combined with \gaia/\tgas, these results provide a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our results have caveats.
Any inferences based upon these results should be made with the recognition of those caveats,
and acknowledge that they are subject to our explicit assumptions.

@@

% Caveats in the results:
% MULTIPLE MODELS
% HETEROGENEOUS TRAINING SET
% METAL POOR ABUNDANCES

% UNSURE IF TWO ABUNDANCE SCALES ARE ON THE SAME SCALE --!
% even if they are on the same scale...
% metal-poor dwarfs/sub-giants

% quality constraints recmomended
% recommended SNR and chi-sq etc
% weird projections in space. --> use morphological classifications to guide

% despite these limitations, this catalog is the largest??? of abundances.
% in the future we will do spectrophotometric distances to improve on this

\section{Conclusion}
\label{sec:conclusion}

We performed an independent analysis of \rave\ spectra using a data-driven approach.
We report effective temperature $\teff$, surface gravity $\logg$, and metallicity [Fe/H]
for X stars on the main-sequence and sub-giant branch.  For another X stars on the red
giant branch, we deliver $\teff$, $\logg$, and a total of X.XX~million elemental abundances:
O, Mg, Al, Ca, Si, Fe, and Ni for X stars.

% Cross-validation, and
% Validate through literature comparisons

\stub{Typical precision}
\stub{Something about exoplanet host stars, TESS, etc}

This catalog constitutes the largest collection of stellar abundances for stars in the
first \gaia\ data release.  When combined with positions and 3D velocities from \gaia,
we hope the \project{unRAVE} catalog will help advance understanding of the Milky Way's
formation and evolution.

>>>>

We have presented an independent re-analysis of \rave\ spectra that makes near-maximal
use of the information content for red giant branch stars, and provides a significant
improvement in stellar parameters ($\teff$, $\logg$, [Fe/H]) over previous \rave\ data
releases.  When combined with the \tgas\ sample, these results may amount to a powerful
compendium for chemo-dynamic studies of the Milky Way.  However, our analysis has caveats.
Any inferences based upon these results should be made with the recognition of those caveats,
and acknowledge that they are subject to our explicit assumptions, some of which are 
provably incorrect.

\stub{assumptions that are provably wrong: accurate labels in the training set. lol}

@@

\stub{Metallicities on the main-sequence and giant branch -- we cannot be sure if they
are correct. Are there any indications that we can get which suggest whether they are
good or bad?}

For some of the most metal-poor giant stars in \rave\, we \emph{know} the abundances 
are not on the same scale as \apogee, because we were forced to adopt abundances for 
specific elements when they were unavailable.  Although we sought to adopt the mean
level of Galactic chemical enrichment at the overall metallicity, this is not a
representative abundance. Even if that is the \emph{mean} enrichment at that Galactic
metallicity, there is no requirement for zero abundance spread.
More fundamentally, we are incorrectly assuming that the element \emph{must} be 
detectable in the photosphere of the star.  There may be no transition that is 
detectable in that star, even with zero noise, because it is too weak to have any 
effect on the spectrum.  In the most optimistic case, this can be considered to be
forcing the model to make use of correlated information between abundances.  In a
more representative (pessimistic) case, we are simply invoking what all abundances
should be at low metallicity.

This choice is reflected in the abundances of the test set.  While we do recover
trustworthy metallicities for ultra metal-poor ($[{\rm Fe/H}] \lesssim -4$) stars like 
CD-38~245, the individual abundances for all extremely metal-poor stars aggregate
(in [X/Fe] space; Figure~\ref{fig:gce}) at the assumed abundances for the metal-poor
stars in our sample.  Thus, while the overall metallicities appear reliable, the 
individual abundances for extremely metal-poor stars in the test set cannot be
considered trustworthy in any sense.  For this reason we have updated the electronic
catalog to discard these results, and included a quality control flag to indicate
the result was discarded (see catalog \texttt{README} file for specifics related to
the data structure and content).

\stub{assumptions that are provably wrong: RAVE spectral resolution}

\stub{assumptions that are provably wrong: correlated noise in the RAVE spectra -- this is minor and unlikely to cause a real issue}

\stub{assumptions that are probably wrong: fringing in high S/N spectra produces issues with the normalization and thus the spectrum. KCF to comment more on this}

\stub{weird projections in the data space --> use morphological classifications to guide}

\stub{quality constraints, etc}

\stub{despite limitations, this catalog may be useful for science. N of abundances}

\stub{in the future we will do spectrophotometric distances to improve on this}

This catalog constitutes the largest collection of stellar abundances for stars in the
first \gaia\ data release.  When combined with positions and 3D velocities from \gaia,
we are optimistic that the \project{unRAVE} catalog will help advance understanding 
of the Milky Way's formation and evolution.
